---
title: "Data Analysis of Apple Daily"
author: "Jean Lin"
date: "Saturday, March 21, 2015"
output: ioslides_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
library(XML)
extract.webpage = function(link, tag.path){
    webpage = readLines(url(link))
    htmlpage = htmlParse(webpage, asText = TRUE)
    tag.values = xpathSApply(htmlpage, tag.path, xmlValue)
    
    tag.values
}

# get all donation ID, date and amount
get.donation.progress = function(){
    donation.progress = data.frame(matrix(ncol = 3, nrow = 10))
    colnames(donation.progress) = c("projectID", "date", "amount")
    index = 1
    for(i in 1:173){
        link = paste("http://search.appledaily.com.tw/charity/projlist/Page/", i, sep = "")
        tag.path = "//td"
        
        #get the web page content
        tag.values = extract.webpage(link, tag.path)
        
        #get the project ID and donation amount
        for(j in seq(from = 2, to = length(tag.values), by = 6)){
            if(tag.values[j+3] == "已結案"){
                donation.progress[index, "projectID"] = tag.values[j]
                donation.progress[index, "date"] = tag.values[j+2]
                donation.progress[index, "amount"] = as.integer(tag.values[j+4])
                index = index + 1 
            }
        }
        
    }
    write.csv(donation.progress, "donation_progress.csv", row.names = F)
    
    donation.progress
}

```


## Brief View of All Donation Amount

```{r, echo=FALSE}
boxplot(donation.progress$amount, horizontal = TRUE)
```

## Eliminating the Special Event

- `r donation.progress[2870, "projectID"]`
- `r donation.progress[2869, "projectID"]`

```{r, echo=FALSE}
donation.progress = donation.progress[-c(2870, 2869),]
boxplot(donation.progress$amount, horizontal = TRUE)
```

## Donation Amount Statistics

- Mean: `r sprintf("%.2f", mean(donation.progress$amount))`
- Median: `r sprintf("%.2f", median(donation.progress$amount))`
- Min.: `r sprintf("%.2f", min(donation.progress$amount))`
- Max.: `r sprintf("%.2f", max(donation.progress$amount))`
- SD.: `r sprintf("%.2f", sd(donation.progress$amount))`

## Donation Amount Distribution

```{r, echo=FALSE}
hist(donation.progress$amount, breaks = 50)
```

## Donation Amount Trend
```{r, echo=FALSE}
donation.progress$date = as.Date( donation.progress$date, '%Y/%m/%d')
donation.progress$amount = as.integer(donation.progress$amount)
donation.progress$year = as.factor(format(donation.progress$date, "%Y"))
require(ggplot2)
g = ggplot( data = donation.progress, aes( date, amount ))
g + geom_point()
```

