---
title: "Data Analysis of Apple Daily"
author: "Jean Lin"
date: "Saturday, March 21, 2015"
output: ioslides_presentation
---

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
library(XML)
extract.webpage = function(link, tag.path){
    webpage = readLines(url(link))
    htmlpage = htmlParse(webpage, asText = TRUE)
    tag.values = xpathSApply(htmlpage, tag.path, xmlValue)
    
    tag.values
}

# get all donation ID, date and amount
get.donation.progress = function(){
    donation.progress = data.frame(matrix(ncol = 3, nrow = 10))
    colnames(donation.progress) = c("projectID", "date", "amount")
    index = 1
    for(i in 1:173){
        link = paste("http://search.appledaily.com.tw/charity/projlist/Page/", i, sep = "")
        tag.path = "//td"
        
        #get the web page content
        tag.values = extract.webpage(link, tag.path)
        
        #get the project ID and donation amount
        for(j in seq(from = 2, to = length(tag.values), by = 6)){
            if(tag.values[j+3] == "已結案"){
                donation.progress[index, "projectID"] = tag.values[j]
                donation.progress[index, "date"] = tag.values[j+2]
                donation.progress[index, "amount"] = as.integer(tag.values[j+4])
                index = index + 1 
            }
        }
        
    }
    write.csv(donation.progress, "donation_progress.csv", row.names = F)
    
    donation.progress
}

```


## Brief View of All Donation Amount

```{r, echo=FALSE}
boxplot(donation.progress$amount, horizontal = TRUE)
```

## Eliminating the Special Event

- `r donation.progress[2870, "projectID"]`
- `r donation.progress[2869, "projectID"]`

```{r, echo=FALSE}
donation.progress = donation.progress[-c(2870, 2869),]
boxplot(donation.progress$amount, horizontal = TRUE)
```

## Donation Amount Statistics

- Mean: `r sprintf("%.2f", mean(donation.progress$amount))`
- Median: `r sprintf("%.2f", median(donation.progress$amount))`
- Min.: `r sprintf("%.2f", min(donation.progress$amount))`
- Max.: `r sprintf("%.2f", max(donation.progress$amount))`
- SD.: `r sprintf("%.2f", sd(donation.progress$amount))`

## Donation Amount Distribution

```{r, echo=FALSE}
hist(donation.progress$amount, breaks = 50)
```

## Donation Amount Trend
```{r, echo=FALSE}
donation.progress$date = as.Date( donation.progress$date, '%Y/%m/%d')
donation.progress$amount = as.integer(donation.progress$amount)
donation.progress$year = as.factor(format(donation.progress$date, "%Y"))
require(ggplot2)
g = ggplot( data = donation.progress, aes( date, amount ))
g + geom_point()
```

## Donation Behavior in 2008

```{r, echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE}
#run get.donation.count() @donationSN.R
donor.count = read.csv("donor_count.csv", header = T, stringsAsFactors = F)


gen.event.matrix = function(start.proj, end.proj, filepath){
    #order aid by published date
    dt.published.ordered = donationData[with(donationData, order(dt.published)), c("aid", "dt.published")]
    
    #get the start date of the donation event
    donation.details = read.csv(paste(filepath, dt.published.ordered[start.proj,"aid"], ".csv", sep=""), header = T, stringsAsFactors = F)
    donation.details$Date = as.Date(donation.details$Date)
    start.date = min(donation.details$Date)
    
    #get the end date of donation event
    donation.details = read.csv(paste(filepath, dt.published.ordered[end.proj,"aid"], ".csv", sep=""), header = T, stringsAsFactors = F)
    donation.details$Date = as.Date(donation.details$Date)
    end.date = max(donation.details$Date)
    
    # for event matrix data structurej
    event.matrix = matrix(data = 0, ncol = as.integer(end.date - start.date)+1 , nrow = nrow(donor.count))
    row.names(event.matrix) = donor.count$Name
    colnames(event.matrix) = as.character(seq(from = start.date, to = end.date, by="day"))
    
    for(k in start.proj:end.proj){
        #print(dt.published.ordered[k,"aid"])
        donation.details = read.csv(paste(filepath, dt.published.ordered[k,"aid"], ".csv", sep=""), header = T, stringsAsFactors = F)
        donation.details$Date = strftime(donation.details$Date, "%Y-%m-%d")
        
        for(i in 1:nrow(donation.details)){
            donor.names = unlist(strsplit(donation.details[i, "Name"], "、"))
            
            for(j in seq(donor.names)){
                event.matrix[donor.names[j], donation.details[i,"Date"]] = event.matrix[donor.names[j], donation.details[i,"Date"]] + 1
            }
        }
    }
    
    event.matrix   
}

#generate donation event matrix in 2008
event.matrix.2008 = gen.event.matrix(start.proj = 1, end.proj = 288, filepath = "./donation_details/")
donor.count.2008 = apply(event.matrix.2008, 1, sum)
month.active.donor = names(donor.count.2008[donor.count.2008  == 12])
```

- There are 246 people who made donation exactly 12 times
- Donation behavior of `r month.active.donor[123]` as example

```{r, echo=FALSE}
plot(event.matrix.2008[month.active.donor[123],] ~ as.Date(colnames(event.matrix.2008)), type = "l")
```



